Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-12-07 bayesian-analysis/kundinger-submit.tex
fixing typos.

With all record pairs converted to hashed values, we can create a more compact nested list 
$$\mathcal{R} = \left\{\{r_{j_p} \}_{p=1}^{P} \right\}_{j = 1}^{n_2}$$
where $r_{j_p} = \{i \in \bm{X_1} | (i, j) \in h_p\}$. This representation is useful because it allows us to easily compute sufficient statistics
$$H_{j_p} = \sum_{i} I((i, j) \in h_p) = ||r_{j_p}||$$
and
$$H_p =  \sum_{i, j} I((i, j) \in h_p) = \sum_{j} H_{j_p}$$
For convenience, denote this set of sufficient statistics $\mathcal{H} = \left\{\{H_{j_p}\}, \{H_{p}\}\right\}.$ As we will shown in Section \ref{efficient-posterior}, all posterior calculations are conducted with these sufficient statistics. Note that $\mathcal{P}$, $\mathcal{R}$, and $\mathcal{H}$  fully characterize the comparison matrix $\Gamma$ with no loss of information, so we proceed with $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{H}\}$ for posterior inference.

@@

Instead, we use one-hot encodings of the agreement patterns $\mathcal{P}$ for more efficient calculations. Denote
$H_p^m = \sum_{j=1}^{n_B} \bm{1}_{(Z_j, j) \in h_p}$ to be the
number of matching record pairs with agreement pattern $p$. We also can easily calculate the number of non-matching record pairs with agreement pattern $p$ as \(H_p^u = H_p - H_p^m\). Then, if $\bm{\alpha_0}$ and $\bm{\beta_0}$ are vectors of prior parameters for the $\bm{m}$ and $\bm{u}$ distributions respectively, the posterior update becomes

$$\bm{\alpha(Z)} = \bm{\alpha_0} + \sum_{p=1}^P H_p^m \times h_p$$
$$\bm{\beta(Z)} = \bm{\beta_0} + \sum_{p=1}^P H_p^u \times h_p.$$
These constitute $\tilde{L}$ summations over $P$ quantities, where $\tilde{L} = \sum_{f=1}^F L_f$ is the total number of levels used across all features in the linkage task.

@@

We demonstrate the speed, and accuracy of \texttt{fabl} as compared to \texttt{BRL} through several simulation studies.

>>>>

With all record pairs converted to hashed values, we can create a more compact nested list 
$$\mathcal{R} = \left\{\{r_{j_p} \}_{p=1}^{P} \right\}_{j = 1}^{n_2},$$
where $r_{j_p} = \{i \in \bm{X_1} | (i, j) \in h_p\}$. This representation is useful because it allows us to easily compute sufficient statistics
$$H_{j_p} = \sum_{i} I((i, j) \in h_p) = ||r_{j_p}||$$
and
$$H_p =  \sum_{i, j} I((i, j) \in h_p) = \sum_{j} H_{j_p}$$
For convenience, denote this set of sufficient statistics $\mathcal{H} = \left\{\{H_{j_p}\}, \{H_{p}\}\right\}.$ As we will shown in Section \ref{efficient-posterior}, all posterior calculations are conducted with these sufficient statistics. Note that $\mathcal{P}$, $\mathcal{R}$, and $\mathcal{H}$  fully characterize the comparison matrix $\Gamma$ with no loss of information, so we proceed with $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{H}\}$ for posterior inference.

@@

Instead, we use one-hot encodings of the agreement patterns $\mathcal{P}$ for more efficient calculations. Denote
$H_p^m = \sum_{j=1}^{n_B} \bm{1}_{(Z_j, j) \in h_p}$ to be the
number of matching record pairs with agreement pattern $p$. We also can easily calculate the number of non-matching record pairs with agreement pattern $p$ as \(H_p^u = H_p - H_p^m\). Then, if $\bm{\alpha_0}$ and $\bm{\beta_0}$ are vectors of prior parameters for the $\bm{m}$ and $\bm{u}$ distributions respectively, the posterior update becomes
$$\bm{\alpha(Z)} = \bm{\alpha_0} + \sum_{p=1}^P H_p^m \times h_p$$
$$\bm{\beta(Z)} = \bm{\beta_0} + \sum_{p=1}^P H_p^u \times h_p.$$
These constitute $\tilde{L}$ summations over $P$ quantities, where $\tilde{L} = \sum_{f=1}^F L_f$ is the total number of levels used across all features in the linkage task.

@@

We demonstrate the speed and accuracy of \texttt{fabl} as compared to \texttt{BRL} through several simulation studies.
